%________________________________________________________________________________
% @brief    LaTeX2e Resume for Abhishek Chanda
\documentclass[margin,line]{resume}


%________________________________________________________________________________
\begin{document}
\name{\Large Abhishek Chanda}
\begin{resume}

%    %____________________________________________________________________________
%    % Contact Information
%    \section{\mysidestyle Contact\\Information}
%
%    WINLAB                            \\%\hfill office: +1 (732) 932-6857          \vspace{0mm}\\\vspace{0mm}%
%    Rutgers, The State University of New Jersey                          \hfill mobile: +1 (940) 613-9161          \vspace{0mm}\\\vspace{0mm}%
%    92 Phelps Avenue, Apt D, New Brunswick, NJ 08901      \hfill e-mail: abhishek.becs@gmail.com  \vspace{0mm}\\\vspace{-4.5mm}%

    %__________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    1247 Vicente Dr, Apt 96                         \hfill mobile: +1 (940) 613-9171          \vspace{0mm}\\\vspace{0mm}%
    Sunnyvale, CA 94086      \hfill e-mail: abhishek.becs@gmail.com  \vspace{0mm}\\\vspace{-6mm}%

    %__________________________________________________________________________
%Objective
%\section{\mysidestyle Objective}
%Seeking a challenging position as a Software Engineer 
% where I can contribute my skills to help the company to acheive it's goals and to grow along with it.

    %__________________________________________________________________________
    % Research Interests
    %\section{\mysidestyle Research\\Interests}

   %My research interests are in wireless networking and mobile computing. Currently, my
%research focuses on routing and transport in hybrid, disconnected networks. I am also interested
%in sensor networks and their applications.

    %__________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{WINLAB, Rutgers University}\\ %\vspace{2mm}\\\vspace{1mm}%
    \textsl{MS, Electrical and Computer Engineering} \hfill \textbf{ August 2010 -- May 2013}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Advisor:  Professor Dipankar Raychaudhuri
	%\item Current GPA: 3.188
    \end{list2}\vspace{-1.5mm}

    \textbf{Bengal Engineering and Science University}, India \\%\vspace{2mm}\\\vspace{1mm}%
    \textsl{BE, Computer Science and Technology} \hfill \textbf{ August 2004 -- August 2008}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Advisor:  Professor Abhik Mukherjee
	%\item GPA: 78/100
    \end{list2}\vspace{-1.5mm}

    %__________________________________________________________________________________
    % Honours and Awards
  \section{\mysidestyle Honours and\\Awards} 

    Graduate Research Assistantship at Rutgers University \hfill \textbf{September 2010 -- May 2012}
    %___________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

\textbf{Cloudscaling}, CA, USA\\
\textsl{Software Engineer} \hfill \textbf{June 2013 -- Present}\\%\vspace{-3mm}
I am involved in design and implementation of scalable networking solutions around OpenStack.

\textbf{Huawei Technologies}, CA, USA\\
\textsl{Research Intern} \hfill \textbf{June 2012 -- December 2012}\\\vspace{-3mm}
\begin{list2}
\item \textbf{Content Oriented Network Architecture:}\\
Designed and implemented a Content Distribution Network based on OpenFlow. For prototyping, I wrote a cache in C++ and a TCP proxy in Python from scratch, used Open vSwitch as the forwarding engine and Floodlight as the controller. This work resulted in a number of publications and a patent.
\end{list2}

    \textbf{WINLAB, Rutgers University}, NJ, USA \\
    \textsl{Graduate Research Assistant} \hfill \textbf{August 2010 -- May 2012}\\\vspace{-3mm}
    \begin{list2}
        \item \textbf{MobilityFirst (August 2010 -- May 2012):}\\
	This is a NSF sponsored future Internet architecture project where we designed a clean-slate architecture for the future Internet. I was responsible for intra domain routing and transport architecture. We used C++ and Python code on NS3 to evaluate our design. This work has resulted in two paper publications and one poster presentation.
        \item \textbf{TerraPIN (January 2012 -- May 2012):}\\
	We designed and prototyped a smart content distribution system based on smart phones. I have built a prototype on Android with the backend in PHP and SQLite. This app along with RESTful API for the service will be released in the market soon.
    \end{list2}

    \textbf{Microsoft IT India}, Hyderabad, India \\%\vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Test Engineer} \hfill \textbf{August 2008 -- July 2010}\\
    I was involved with a project where we re-designed Microsoft's existing product distribution system to make it more scaleable. The system was implemented on .Net and SQL Server using C\#. As a part of the test team, I was responsible for manual and automated testing of some key components of the system. I designed and developed a test harness based on Visual Studio 2010 and some of Microsoft's internal tools.

    %________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Implementation Skills} 

    \textbf{Programming languages}\\
Python, Ruby, Bash scripting, Java, C, C++, SQL

    \textbf{Platforms and technologies}
\begin{list2}
\item Cloud computing platforms like OpenStack, AWS, Apach Mesos etc.
\item Infrastructure provisioning systems like Chef, fabric etc.
\item Extensive experience in packet processing with C and C++
\item Network protocols and concepts like TCP/IP, UDP, DNS, HTTP, SSL, IPSEC, DHCP, SSL, REST, SOAP, routing, transport, firewalls, cloud computing, virtualization, web caching and proxy
\item Network programming and distributed systems implementation on Linux and Unix
\item Networking tools like Wireshark, tcpdump, iptables, netfilter, netlink etc.
\item Software defined networking and network function virtualization with OpenFlow using Open vSwitch and with OpenContrail.
\newpage
\item Android based mobile programming.
\item Virtualization using VirtualBox, KVM and Qemu.
\item Version control systems like git and SVN.
\end{list2}

%\newpage

%    \textbf{Platforms and tools}\\
%NS2 and 3, GNUPlot, .Net, Android, Visual Studio and network tools on Unix/Windows, SVN, Git, Amazon AWS and EC2, vi, GDB, Open vSwitch, Floodlight controller


    %______________________________________________________________________________
    % Publications
    \section{\mysidestyle Selected Publications}

Abhishek Chanda, Cedric Westphal,
``ContentFlow: Adding content primitives to software defined networks",
\textsl{IEEE Globecom}, 2013.

\vspace{-2mm}
Abhishek Chanda, Cedric Westphal, Dipankar Raychaudhuri,
``Content Based Traffic Engineering in Software Defined Information Centric Networks",
\textsl{IEEE NOMEN}, 2013.

\vspace{-2mm}
    Nehal Somani, Abhishek Chanda, Samuel C. Nelson, Dipankar Raychaudhuri,
    ``Storage-Aware Routing for Robust and Efficient Services in the Future Mobile Internet'',
    \textsl{IEEE FutureNet}, 2012.

\vspace{-2mm}
    Gautam Bhanage, Abhishek Chanda, Jun Li, Dipankar Raychaudhuri,
    ``Storage-Aware Routing Protocol for the MobilityFirst Network Architecture'',
    \textsl{European Wireless}, pp. 1--8, 2011.

\vspace{-2mm}
   Abhishek Chanda, Abhik Mukherjee,
    ``A Hardware Authentication Architecture for Pervasive Devices'',
    \textsl{Hack.In},  2009.

\vspace{-2mm}
    Soma Bandyopadhyay, Nirupam Roy, Aritra Banerjee, Abhishek Chanda, Abhik Mukherjee and SS Barat,
    ``RFID enabled navigation system of an autonomous robotic guide'',
    \textsl{CSI Communications: Special Issue in Robotics}, Vol 32 No 8, pp 24--27, November 2008.

%_____________________________________________________________________________
% Poster and demo abstracts

\section{\mysidestyle Poster and Demo abstracts}
Abhishek Chanda and Cedric Westphal, ``A Content Management Layer for Software Defined Information Centric Networks (demo abstract)", \textsl{ICN}, 2013.

 \vspace{-2mm}
    Abhishek Chanda, Samuel C. Nelson, Gautam Bhanage, Dipankar Raychaudhuri,
    ``ByPass: A Unified Transport Protocol for the Internet (poster abstract)'',
    \textsl{HotMobile Poster Session},  2012.

\vspace{-2mm}
Abhishek Chanda, Samuel C. Nelson, Gautam Bhanage, Dipankar Raychaudhuri,
    ``ByPass: towards an unified transport protocol for the internet (extended abstract)'',
    \textsl{SIGMOBILE Mobile Computing and Communication Review},  2012.


%_____________________________________________________________________________
% Patents

\section{\mysidestyle Patent application}
C. Westphal and A. Chanda, ``Content Based Traffic Engineering in Software Defined Information Centric Networks", \textsl{US20140173018 A1}, 2013

\section{\mysidestyle Open source contributions}
OpenStack, Apache Mesos, OpenContrail, Fog, Eventlet

    %___________________________________________________________________________
    % Academic services
    \section{\mysidestyle Academic\\Services}
\begin{list2}
\item Invited peer reviewer for IEEE Wireless Communications Magazine
\item Invited peer reviewer for IEEE Transactions on Mobile Computing
\item Invited peer reviewer for IEEE Computational Intelligence and Communication Networks 2014
\item Invited peer reviewer for IEEE PIMRC 2015
\item Invited peer reviewer for IEEE Network Magazine
\item Invited peer reviewer for Elsevier Computer Networks
\item TPC member for Communication Systems and Network Technologies 2015
\item TPC member for World Symposium of Computer Applications and Research 2015
\end{list2}

%\newpage

%-------------------------------------------------------------------------
%
\section{\mysidestyle Relevant Courses} 
\begin{list2}
\item \textbf{Graduate courses:}\\
Communication Networks, Wireless Communications, Stochastic Signals and Systems, Advanced Computer Architecture, System Analysis, Algorithms and Data Structures\\

\item \textbf{Undergraduate courses:}\\
Data Structures and Algorithms, Algorithms, Computer Architecture, Networking, Operating System, Compilers, Operations research, Object oriented design methodology, Graph theory, Discrete algebra
\end{list2}
    %______________________________________________________________________________
    % Referees
%    \section{\mysidestyle Referees} 
%    {\sl Available on request.}

\section{\mysidestyle Selected academic projects}
\begin{list2}
	\item Designed and implemented a `k out of m' routing protocol with support for multicasting on linux platform in C++
	\item Designed and implemented a content sharing platform on Android phones. This system allows users to dynamically generate content and share with a selected set of peers securely over the Internet
\end{list2}

\section{\mysidestyle Professional memberships}
IEEE, ACM

%__________________________________________________________________________
\section{\mysidestyle References} 
 \sl Available on request.

%Professor Dipankar Raychaudhuri\\
%		\sl{ray@winlab.rutgers.edu}\\

%Professor Yanyong Zhang\\
%		\sl{yyzhang@winlab.rutgers.edu}


%__________________________________________________________________________
\end{resume}
\end{document}


%__________________________________________________________________________
% EOF

